# Criteria

## Cells
The quality of cells was then assessed based on two metrics: 
(1) Cells with detected genes fewer than 200 were filtered out in the function "CreateSeuratObject". (The number of detected genes per cell;)
(2) Cells that have less than 20% proportion of mitochondrial genes were filtered out. Some studies do not have mitochondrial genes. It seems mitochondrial genes might have been removed by the original authors because of technical influences.
(3) To remove the potential doublets for datasets that do not have annotation (need to QC by ourselves), we will use DoubletFinder-R based (DoubletDetection or Scrublet(python)). Waiting the metadata first.

```{r include=FALSE}
# data import
health_list_1115<-qread("/fs/ess/PAS1475/guoqi/sci_atlas/raw_data/health_list_1115.qs")

#check mit
health_list_1115_qc<-list()
for(i in 1:length(health_list_1115)){
  print(grep ("^mt-", rownames(health_list_1115[[i]][["RNA"]]),value = T))
#some of them have, so we do QC separately
for(i in 1:length(health_list_1115)){
  Idents(health_list_1115[[i]])<-health_list_1115[[i]]$Species
  health_list_1115[[i]][["percent.mt"]] <-PercentageFeatureSet(health_list_1115[[i]], pattern = "^mt.")
  health_list_1115_qc[[i]]<-subset(  health_list_1115[[i]], subset = nFeature_RNA > 200 & percent.mt < 20)
}
```

## Genes
1. The genes detected in more than 3 cells were retained. (This is done in the function "CreateSeuratObject")
2. Intersect genes among all datasets have been used to avoid inconsistent gene names issues.

```{r Genes, include=FALSE}
# intersect gene names
## Get intersect gene names
gene_list_genesymbol<-list()
for(i in 1:length(health_list_1115)){
  gene_hugo<-rownames(health_list_1115[[i]])
  gene_list_genesymbol[[i]]<-gene_hugo
}
## subset matrix with intersect gene names
intersect_genesymbol<-Reduce(intersect, gene_list_genesymbol)#10174
health_list_1115_qc_intersect<-list()
for(i in 1:length(health_list_1115_qc)){
  #subset based on the intersect gene list
  health_list_1115_qc_intersect[[i]]<-subset(health_list_1115_qc[[i]],features =intersect_genesymbol)
}
```

# Merge after QC

```{r include=FALSE}
#merge into one for QC
health_merge_1115_qc_intersect <- Merge_Seurat_List(
  health_list_1115_qc_intersect,
  add.cell.ids = NULL,
  merge.data = TRUE
)
qsave(health_merge_1115_qc_intersect,"/fs/ess/PAS1475/guoqi/sci_atlas/raw_data/health_merge_qc_1115_intersectgene.qs")
```
